Tutorial: SQL-on-Hadoop Systems

### 2015-04-01 paper.tex
commit

Spark is a fast general purpose cluster computing engine that is compatible with Hadoop data.  There are three different systems that use Spark as their run-time for SQL processing: Shark \cite{sharksigmod13}, Hive on Spark \cite{hiveOnSpark}, and Spark SQL \cite{sparkSQL}. Shark replaces the MapReduce run-time of Hive \cite{hive} with Spark. It is still uses the Hive compiler, and interfaces but genereates Spark jobs. Hive on Spark is another attempt at replacing MapReduce/Tez based run-times of Hive with Spark. Spark SQL uses the Shark \cite{sharksigmod13} run-time but replaces the HiveQL and compiler with SQL, and a new compiler that uses the catalyst query optimizer.

>>>>

Spark is a fast general purpose cluster computing engine that is compatible with Hadoop data.  There are three different systems that use Spark as their run-time for SQL processing: Shark \cite{shark}, Hive on Spark \cite{hiveSpark}, and Spark SQL \cite{sparkSQL}. Shark replaces the MapReduce run-time of Hive \cite{hive} with Spark. It is still uses the Hive compiler, and interfaces but genereates Spark jobs. Hive on Spark is another attempt at replacing MapReduce/Tez based run-times of Hive with Spark. Spark SQL uses the Shark \cite{shark} run-time but replaces the HiveQL and compiler with SQL, and a new compiler that uses the catalyst query optimizer.
